Geometric variational problems

### 2020-11-15 NSF2020/Description/newspecificaim2.tex
fixed typos in SA 2 and 3

\subsection{Specific Aim 2: Efficient high-order numerical methods for
large-scale simulations}
\label{subsec:specific_aim_2}
%\begin{figure}[h]
\begin{wrapfigure}[13]{r}{0.61\textwidth}
  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
    \vspace{-20pt}
    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
    the Stokes equations, and the hydrophobic forces depend on the
    solvent activity that satisfies the screened Laplace equation. The
    geometry is updated by solving the mobility problem.} 
\end{wrapfigure}
%\end{figure}
% ----------------------------------------------------------------------
Over the past decade, there has been an explosion of interest in
small-scale processes that utilize capillary forces and van der Waals
interactions to coordinate movement
and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
Additionally, hydrodynamic interactions are central to fabricating complex,
three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
Hydrodynamic effects cannot
be ignored since they, like the rates of biological functions like fusion,
fission, and pore dynamics, determine rely on viscous
dissipation~\cite{RYHAM20112929}.
%
In Specific Aim 2, we propose to develop efficient high-order numerical
methods to simulate dynamic assembly of particles under HAP potential in
a viscous solvent. 
%
%
%hydrodynamics effects by em
%particles in a solvent. 
%
% Results from these proposed numerical simulations will be useful to 
% Finally, coarse-grained and molecular
%dynamics theories include water either explicitly or implicitly in their
%models. 
%
%The immediate goal of the present proposal is to simulate
%vesicle bilayers in external flows, where the bilayers are represented
%by a self-assembled collection of rigid particles.
%
As described in~\eqref{eq:stokes} and illustrated in
Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
equations for an incompressible, viscous fluid, and these equations are
coupled to the screened-Laplace equation~\eqref{SL} through viscous and
hydrophobic stress balance.

>>>>

\subsection{Specific Aim 2: Efficient high-order numerical methods for
large-scale simulations}
\label{subsec:specific_aim_2}
%\begin{figure}[h]
\begin{wrapfigure}[13]{r}{0.61\textwidth}
  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
    \vspace{-20pt}
    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
    the Stokes equations, and the hydrophobic forces depend on the
    solvent activity that satisfies the screened Laplace equation. The
    geometry is updated by solving the mobility problem.} 
\end{wrapfigure}
%\end{figure}
% ----------------------------------------------------------------------
Over the past decade, there has been an explosion of interest in
small-scale processes that utilize capillary forces and van der Waals
interactions to coordinate movement
and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
Additionally, hydrodynamic interactions are central to fabricating complex,
three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
Hydrodynamic effects cannot
be ignored since they, like for the rates of biological functions 
like pore dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
%
In Specific Aim 2, we propose to develop efficient high-order numerical
methods to simulate dynamic assembly of particles under HAP potential in
a viscous solvent. 
%
%
%hydrodynamics effects by em
%particles in a solvent. 
%
% Results from these proposed numerical simulations will be useful to 
% Finally, coarse-grained and molecular
%dynamics theories include water either explicitly or implicitly in their
%models. 
%
%The immediate goal of the present proposal is to simulate
%vesicle bilayers in external flows, where the bilayers are represented
%by a self-assembled collection of rigid particles.
%
As described in~\eqref{eq:stokes} and illustrated in
Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
equations for an incompressible, viscous fluid, and these equations are
coupled to the screened-Laplace equation~\eqref{SL} through viscous and
hydrophobic stress balance.
